Introducing ICBe: Very High Recall and Precision Event Extraction from Narratives about International Crises

### 2022-09-12 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.Rmd
supplemental authors

The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history, $Pr(H|E)$. It does little good to recall a historical event but too vaguely (e.g. MIDs describes the Cuban Missile crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g. ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019) to be useful for downstream applications. ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable. You should be able to lay out events of a crisis on a timeline, as in Figure 3 and Figure 4, and read off the macro structure of an episode from each individual move. We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig. D3 and D4) and all crises on the companion website.

@@

\begin{figure}[H]
\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
\end{figure}

@@

Funding {#format .unnumbered}
========================================

@@

Acknowledgements {#format .unnumbered}
========================================
  We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort. We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.  We thank the many undergraduate coders for their patience and dedication. Thanks to the Center for Peace and Security Studies and its membership for comments. Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback. Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang. This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.

Author Contributions {#format .unnumbered}
========================================
Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D., T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.; Visualization: R.W.D., T.L.S.; Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.; Funding Acquisition: E.G., J.L.

Data Availability Statement {#format .unnumbered}
========================================
This article’s data, online appendix, replication material, and visualizations of every historical episode are available on the github repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website www.crisisevents.org.

Conflicts of Interests {#format .unnumbered}
========================================
There are no conflicts of interest to disclose.

&nbsp;

>>>>

The other side of event measurement is precision, the degree to which a sequence of events correctly and usefully describes the information in history, $Pr(H|E)$. It does little good to recall a historical event but too vaguely (e.g. MIDs describes the Cuban Missile crisis as a blockade, a show of force, and a stalemate) or with too much error (e.g. ICEWS records 263 "Detonate Nuclear Weapons" events between 1995-2019) to be useful for downstream applications. ICBe's ontology and coding system is designed to strike a balance so that the most important information is recovered accurately but also abstracted to a level that is still useful and interpretable. You should be able to lay out events of a crisis on a timeline, as in Figure 3, and read off the macro structure of an episode from each individual move. We call this visualization a crisis map, a directed graph intersected with a timeline, and provide crisis maps for every event dataset for each case study (SI Appendix, Fig. D3 and D4) and all crises on the companion website.

@@

<!-- \begin{figure}[H] -->
<!-- \caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}} -->
<!-- \centering{\includegraphics[width=17cm]{./p_471_icbe.png}} -->
<!-- \end{figure} -->

@@

Funding {
========================================

@@

Acknowledgements 
========================================
  We thank the ICB Project and its directors and contributors for their foundational work and their help with this effort. We make special acknowledgment of Michael Brecher for helping found the ICB project in 1975, creating a resource that continues to spark new insights to this day.  We thank the many undergraduate coders for their patience and dedication. Thanks to the Center for Peace and Security Studies and its membership for comments. Special thanks to Rebecca Cordell, Philip Schrodt, Zachary Steinert-Threlkeld, and Zhanna Terechshenko for generous feedback. Thank you to the cPASS research assistants that contributed to this project: Helen Chung, Daman Heer, Syeda ShahBano Ijaz, Anthony Limon, Erin Ling, Ari Michelson, Prithviraj Pahwa, Gianna Pedro, Tobias Stodiek, Yiyi 'Effie' Sun, Erin Werner, Lisa Yen, and Ruixuan Zhang. This project was supported by a grant from the Office of Naval Research [N00014-19-1-2491] and benefited from the Charles Koch Foundation's support for the Center for Peace and Security Studies.

Author Contributions 
========================================
Conceptualization: R.W.D., E.G., J.L.; Methodology: R.W.D., T.L.S.; Software: R.W.D.; Validation: R.W.D., T.L.S.; Formal Analysis: R.W.D., T.L.S.; Investigation: S.C., R.W.D., J.A.G., C.K., N.L., E.M., J.M.C.N., D.P., D.Q., J.W.; Data Curation: R.W.D., D.Q., T.L.S., J.W.; Writing - Original Draft: R.W.D., T.L.S.;  Writing - Review & Editing: R.W.D., J.A.G., E.G., T.L.S.; Visualization: R.W.D., T.L.S.; Supervision: E.G.;  Project Administration: S.C., R.W.D., J.A.G., D.Q., T.L.S., J.W.; Funding Acquisition: E.G., J.L.

Data Availability Statement 
========================================
This article’s data, online appendix, replication material, and visualizations of every historical episode are available on the github repository [ICBEventData](https://urldefense.com/v3/__https://github.com/CenterForPeaceAndSecurityStudies/ICBEventData__;!!Mih3wA!WxDJtEczKfxGTh0S2Krunap8ReymFEL5iTWaSfOHeqlSdyfRx77zmjBSWO1OAm13$) and through the companion website www.crisisevents.org.

Conflicts of Interests 
========================================
There are no conflicts of interest to disclose.

\clearpage

Works Cited
========================================
\vspace{0pt}

### 2022-09-12 replication_paper/political_analysis_draft/ICBe_political_analysis_submission_rmd.tex
supplemental authors

The other side of event measurement is precision, the degree to which a
sequence of events correctly and usefully describes the information in
history, \(Pr(H|E)\). It does little good to recall a historical event
but too vaguely (e.g.~MIDs describes the Cuban Missile crisis as a
blockade, a show of force, and a stalemate) or with too much error
(e.g.~ICEWS records 263 ``Detonate Nuclear Weapons'' events between
1995-2019) to be useful for downstream applications. ICBe's ontology and
coding system is designed to strike a balance so that the most important
information is recovered accurately but also abstracted to a level that
is still useful and interpretable. You should be able to lay out events
of a crisis on a timeline, as in Figure 3 and Figure 4, and read off the
macro structure of an episode from each individual move. We call this
visualization a crisis map, a directed graph intersected with a
timeline, and provide crisis maps for every event dataset for each case
study (SI Appendix, Fig. D3 and D4) and all crises on the companion
website.

@@

\begin{figure}[H]
\caption{Crisis Map: Crimea-Donbas  \label{fig:p_471_icbe}}
\centering{\includegraphics[width=17cm]{./p_471_icbe.png}}
\end{figure}

@@

\hypertarget{format}{%
\section*{Funding}\label{format}}
\addcontentsline{toc}{section}{Funding}

@@

\hypertarget{format}{%
\section*{Acknowledgements}\label{format}}
\addcontentsline{toc}{section}{Acknowledgements}

@@

\hypertarget{format}{%
\section*{Author Contributions}\label{format}}
\addcontentsline{toc}{section}{Author Contributions}

@@

\hypertarget{format}{%
\section*{Data Availability Statement}\label{format}}
\addcontentsline{toc}{section}{Data Availability Statement}

@@

\hypertarget{format}{%
\section*{Conflicts of Interests}\label{format}}
\addcontentsline{toc}{section}{Conflicts of Interests}

@@

~

>>>>

The other side of event measurement is precision, the degree to which a
sequence of events correctly and usefully describes the information in
history, \(Pr(H|E)\). It does little good to recall a historical event
but too vaguely (e.g.~MIDs describes the Cuban Missile crisis as a
blockade, a show of force, and a stalemate) or with too much error
(e.g.~ICEWS records 263 ``Detonate Nuclear Weapons'' events between
1995-2019) to be useful for downstream applications. ICBe's ontology and
coding system is designed to strike a balance so that the most important
information is recovered accurately but also abstracted to a level that
is still useful and interpretable. You should be able to lay out events
of a crisis on a timeline, as in Figure 3, and read off the macro
structure of an episode from each individual move. We call this
visualization a crisis map, a directed graph intersected with a
timeline, and provide crisis maps for every event dataset for each case
study (SI Appendix, Fig. D3 and D4) and all crises on the companion
website.

@@

@@

\hypertarget{funding}{%
\section{Funding \{}\label{funding}}

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

@@

\hypertarget{author-contributions}{%
\section{Author Contributions}\label{author-contributions}}

@@

\hypertarget{data-availability-statement}{%
\section{Data Availability
Statement}\label{data-availability-statement}}

@@

\hypertarget{conflicts-of-interests}{%
\section{Conflicts of Interests}\label{conflicts-of-interests}}

@@

\hypertarget{works-cited}{%
\section{Works Cited}\label{works-cited}}

\vspace{0pt}
